---
title: "Receipt analysis (post-study)"
author: "Remco Benthem de Grave"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(magrittr)
library(here)
library(lattice) #density plot
library(car) #qqplot
library(lme4)
library(wordcloud2) 
library(webshot) #for saving wordcloud
library("htmlwidgets")

#read-in the receipts
receipt_data <- read_csv(here("receipt analysis","data","processed","receipt_level_data.csv"))
#read-in the separate purchases
purchase_data <- read_csv(here("receipt analysis","data","processed","purchase_data.csv"))
```

## Descriptives

### Item level descriptives

```{r}
purchase_data %<>%
  mutate(item_group = if_else(str_to_lower(item_product) == "gnocchi", "Cereals & Potatoes", item_group))

purchase_data %<>%
  select(item_group, item_product, item_units, item_weight_g, item_footprint_g_100g) %>%
  mutate(item_group = str_to_title(item_group), item_product = str_to_lower(item_product)) %>% 
  group_by(item_group, item_product) %>%
  summarise(
    quantity = sum(item_units*item_weight_g/1000), #convert to kg
    footprint = sum(item_units*item_weight_g/1000*item_footprint_g_100g/100)
  )

purchase_data %<>% ungroup()

#create a wordcloud with items by quantity
wordcloud_items_quantity <- purchase_data %>%
  rename(word = item_product, freq = quantity) %>%
  arrange(desc(freq)) %>%
  mutate(
    freq = freq/min(freq),
    freq = round(freq)
  ) %>%
  relocate(word, freq) %>%
  wordcloud2()

wordcloud_items_quantity
  
#create a wordcloud with items by foodprint
wordcloud_items_foodprint <- purchase_data %>%
  rename(word = item_product, freq = footprint) %>%
  arrange(desc(freq)) %>%
  mutate(
    freq = freq/min(freq),
    freq = round(freq)
  ) %>%
  relocate(word, freq) %>%
  wordcloud2()

wordcloud_items_foodprint

#descriptives
#total number of items, total weight, total footprint, number of unique items

cat('\n\nNUMBER OF UNIQUE ITEMS\n\n')
purchase_data %>% 
  nrow()

#save wordclouds as png
# webshot::install_phantomjs()
saveWidget(wordcloud_items_quantity, file = here("output","plots","wordcloud_items_quantity.html"), selfcontained = TRUE)
webshot(here("output","plots","wordcloud_items_quantity.html"), file = here("output","plots","wordcloud_items_quantity.png"), delay =5, vwidth = 480, vheight=480)

saveWidget(wordcloud_items_foodprint, file = here("output","plots","wordcloud_items_foodprint.html"), selfcontained = TRUE)
webshot(here("output","plots","wordcloud_items_foodprint.html"), file = here("output","plots","wordcloud_items_foodprint.png"), delay =5)


```


### Receipt level descriptives

```{r receipt descriptives by participant}
receipt_table_data_participant <-
receipt_data %>% 
  mutate(preloaded = ifelse(date_recorded > hh_start, "scanned", "preloaded")) %>% 
  select(user_ID, preloaded, rcpt_CO2_kg:rcpt_items_n) %>% #household_ID,
  #first create totals per participant
  group_by(user_ID, preloaded) %>%
  summarise(
    across(
      rcpt_CO2_kg:rcpt_items_n,
      .fns = list(
        total = sum
      ),
      .names = "{.col}"
    ),
    n_receipts = n()
  ) %>% 
  #for the moment, let's ignore rcpt_CO2_kg and rcpt_weight_kg
  select(-c(rcpt_CO2_kg, rcpt_weight_kg)) %>%
  #pivot data in preparation for statistics
  pivot_longer(cols = !c(user_ID, preloaded), names_to = 'factor', values_to = 'unit') %>%
  #calculate the statistics 
  group_by(preloaded,factor) %>%
  select(-user_ID) %>%
  summarise(
    across(
      unit,
        .fns = list(
          Q0 = min,
          Q1 = ~quantile(., 0.25),
          Q2 = median, 
          Q3 = ~quantile(., 0.75),
          Q4 = max,
          distribution = ~ list(.x) #we will create the distribution graph in a next step
        ),
        .names = "{.fn}"
    ),
  ) 

#make a table of the data distribution per participant
receipt_table_data_participant_GT <-
receipt_table_data_participant %>%
  ungroup() %>%
  #we don't want to show the number of preloaded receipts now (because we'd need to change the preprocessing to identify individual preloaded receipts)
  # filter(!(factor == "n_receipts" & preloaded == "preloaded")) %>%
  filter(!(preloaded == "preloaded")) %>%
  group_by(preloaded) %>%
  gt(rowname_col = "factor") %>%
  # gt::fmt_number(columns = min:max, decimals = 0) %>%
  #creating the distribution graph
  gt_plt_dist(contains("distribution"), type = "boxplot", same_limit = F) %>%
  #apply styling
  text_replace(
    pattern = c("n_receipts", "rcpt_items_n"),
    replacement = c("Receipts (N)", "Items (N)"),
    #replace this pattern in the row labels
    locations = cells_stub(everything())
  ) %>%
    text_replace(
    pattern = c("rcpt_items_n"),
    replacement = c("Items (N)"),
    #replace this pattern in the row labels
    locations = cells_stub(everything())
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = list(cells_column_labels(everything()),cells_row_groups(everything()))
  ) %>% 
  tab_options(data_row.padding = px(3)) %>%
  #add a footnote explaining the stats displayed
  tab_footnote(footnote = md("Q0 = min"), locations = cells_column_labels(Q0)) %>%
  tab_footnote(footnote = md("Q1 = 25th percentile"), locations = cells_column_labels(Q1)) %>%
  tab_footnote(footnote = md("Q2 = median"), locations = cells_column_labels(Q2)) %>%
  tab_footnote(footnote = md("Q3 = 75th percentile"), locations = cells_column_labels(Q3)) %>%
  tab_footnote(footnote = md("Q4 = max"), locations = cells_column_labels(Q4)) %>%
  #add title
  tab_header(
    title = "Receipt descriptives by participant"
  )

receipt_table_data_participant_GT

#save the table
gtsave(receipt_table_data_participant_GT, file = here("output","tables","receipt_table_data_participant_GT.png"))
gtsave(receipt_table_data_participant_GT, file = here("output","tables","receipt_table_data_participant_GT.docx"))
```

```{r receipt descriptives by receipt}
receipt_table_data_receipt <-
receipt_data %>% 
  mutate(preloaded = ifelse(date_recorded > hh_start, "scanned", "preloaded")) %>% 
  select(preloaded, rcpt_CO2_kg:rcpt_items_n) %>% #household_ID,
  
  #for the moment, let's ignore rcpt_CO2_kg and rcpt_weight_kg
  select(-c(rcpt_CO2_kg, rcpt_weight_kg)) %>%
  # #pivot data in preparation for statistics
  pivot_longer(cols = !c(preloaded), names_to = 'factor', values_to = 'unit') %>%
  #calculate the statistics 
  group_by(preloaded,factor) %>%
  summarise(
    across(
      unit,
        .fns = list(
          Q0 = min,
          Q1 = ~quantile(., 0.25),
          Q2 = median, 
          Q3 = ~quantile(., 0.75),
          Q4 = max,
          distribution = ~ list(.x) #we will create the distribution graph in a next step
        ),
        .names = "{.fn}"
    ),
  ) 

#make a table of the data distribution per participant
receipt_table_data_receipt_GT <-
receipt_table_data_receipt %>%
  ungroup() %>%
  #we don't want to show the number of preloaded receipts now (because we'd need to change the preprocessing to identify individual preloaded receipts)
  # filter(!(factor == "n_receipts" & preloaded == "preloaded")) %>%
  filter(!(preloaded == "preloaded")) %>%
  group_by(preloaded) %>%
  gt(rowname_col = "factor") %>%
  # gt::fmt_number(columns = min:max, decimals = 0) %>%
  #creating the distribution graph
  gt_plt_dist(contains("distribution"), type = "boxplot", same_limit = F) %>%
  #apply styling
    text_replace(
    pattern = c("rcpt_items_n"),
    replacement = c("Items (N)"),
    #replace this pattern in the row labels
    locations = cells_stub(everything())
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = list(cells_column_labels(everything()),cells_row_groups(everything()))
  ) %>% 
  tab_options(data_row.padding = px(3)) %>%
  #add a footnote explaining the stats displayed
  tab_footnote(footnote = md("Q0 = min"), locations = cells_column_labels(Q0)) %>%
  tab_footnote(footnote = md("Q1 = 25th percentile"), locations = cells_column_labels(Q1)) %>%
  tab_footnote(footnote = md("Q2 = median"), locations = cells_column_labels(Q2)) %>%
  tab_footnote(footnote = md("Q3 = 75th percentile"), locations = cells_column_labels(Q3)) %>%
  tab_footnote(footnote = md("Q4 = max"), locations = cells_column_labels(Q4)) %>%
  #add title
  tab_header(
    title = "Receipt descriptives by receipt"
  )

receipt_table_data_receipt_GT

#save the table
gtsave(receipt_table_data_receipt_GT, file = here("output","tables","receipt_table_data_receipt_GT.png"))
gtsave(receipt_table_data_receipt_GT, file = here("output","tables","receipt_table_data_receipt_GT.docx"))
```

```{r receipt descriptives combined}

#combine the tables and add a row of totals
receipt_table_data_combined_GT <-
  bind_rows(
    receipt_table_data_participant %>% mutate(id = "participant") %>% select(-c(Q0,Q4,distribution)),
    receipt_table_data_receipt %>% mutate(id = "receipt") %>% select(-c(Q0,Q4,distribution))
  ) %>%
  #round data
  mutate(across(where(is.numeric), ~round(., digits = 0))) %>%
  # #we don't show info for preloaded receipts
  # filter(!(preloaded == "preloaded")) %>%
  # ungroup() %>%
  # select(-preloaded) %>%
  #format the summary stat
  mutate(stat = paste0(Q2," [",Q1,", ",Q3,"]"), .keep = "unused")

#add totals 
receipt_data_total <- 
  receipt_data %>%
  mutate(preloaded = ifelse(date_recorded > hh_start, "scanned", "preloaded")) %>% 
  select(user_ID, preloaded, rcpt_CO2_kg:rcpt_items_n) %>% #household_ID,
  #first create totals per participant
  group_by(preloaded) %>%
  summarise(
    across(
      rcpt_CO2_kg:rcpt_items_n,
      .fns = list(
        total = sum
      ),
      .names = "{.col}"
    ),
    n_receipts = n()
  ) %>% 
  #for the moment, let's ignore rcpt_CO2_kg and rcpt_weight_kg
  select(-c(rcpt_CO2_kg, rcpt_weight_kg)) %>%
  #pivot data in preparation for statistics
  pivot_longer(cols = !c(preloaded), names_to = 'factor', values_to = 'stat') %>%
  #add table id
  mutate(id = "overall")

receipt_table_data_combined_GT <-
  bind_rows(
    receipt_table_data_combined_GT,
    receipt_data_total %>% mutate(stat = paste0(stat))
  ) %>%
  #we don't show info for preloaded receipts
  filter(!(preloaded == "preloaded")) %>%
  ungroup() %>%
  select(-preloaded)

receipt_table_data_combined_GT %<>% 
  pivot_wider(names_from = id, values_from = stat) %>%
  select(factor, overall, participant, receipt) %>%
  rename("Overall" = overall, "By participant" = participant, "By receipt" = receipt) %>%
  ungroup() %>%
  gt(rowname_col = "factor") %>%
  #apply styling
  text_replace(
    pattern = c("n_receipts", "rcpt_items_n"),
    replacement = c("Receipts (N)", "Items (N)"),
    #replace this pattern in the row labels
    locations = cells_stub(everything())
  ) %>%
  text_replace(
    pattern = c("rcpt_items_n"),
    replacement = c("Items (N)"),
    #replace this pattern in the row labels
    locations = cells_stub(everything())
  ) %>%
  # text_replace(
  #   pattern = c("overall", "participant", "receipt"),
  #   replacement = c("Overall", "By participant", "By receipt"),
  #   #replace this pattern in the row labels
  #   locations = cells_column_labels(everything())
  # ) %>%
  # text_replace(
  #   pattern = c("participant", "receipt"),
  #   replacement = c("By participant", "By receipt"),
  #   #replace this pattern in the row labels
  #   locations = cells_column_labels(everything())
  # ) %>%
  # text_replace(
  #   pattern = c("receipt"),
  #   replacement = c("By receipt"),
  #   #replace this pattern in the row labels
  #   locations = cells_column_labels(everything())
  # ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = list(cells_column_labels(everything()),cells_row_groups(everything()))
  ) %>% 
  tab_options(data_row.padding = px(3)) %>%
  #add a footnote explaining the stats displayed
  tab_footnote(footnote = md("median [IQR], IQR = Inter Quantile Range"), locations = cells_column_labels(c(`By participant`, `By receipt`)))

receipt_table_data_combined_GT

#save the table
gtsave(receipt_table_data_combined_GT, file = here("output","tables","receipt_table_data_combined_GT.png"))
gtsave(receipt_table_data_combined_GT, file = here("output","tables","receipt_table_data_combined_GT.docx"))
```

```{r}

```



Those scanned in the app (not the pre-loaded receipts).

```{r}
#number of receipts scanned in app -- this excludes the receipts provided as starting data.


#hh level, user level, receipt level TODO!

cat('\n\nRECEIPT DESCRIPTIVES\n\n')

cat('\n\nNumber of receipts scanned in the app:',receipt_data %>% filter(date_recorded > hh_start) %>% nrow(),'\n\n')

cat('\n\nDescriptives:\n
    (1)number of days after start of participation that the receipt was scanned,\n
    (2)weight-corrected average product footprint in gCO2/100g,\n
    (3)basket footprint in gCO2 (aka. combined carbon footprint of all products in the basket)\n
    (4)basket weight in grams (aka. combined weight of all products in the basket)\n
    (5)number of items on a receipt\n\n
    ')

receipt_data %>% 
  ungroup() %>%
  filter(date_recorded > hh_start) %>% #remove pre-loaded receipts
  select(day_recorded, rcpt_CO2_g_100g, rcpt_CO2_kg, rcpt_weight_kg, rcpt_items_n) %>% 
  summary()
```

```{r}
#boxplots of receipt descriptives
receipt_data %>% 
  ungroup() %>%
  filter(date_recorded > hh_start) %>% #remove pre-loaded receipts
  select(day_recorded, rcpt_CO2_g_100g, rcpt_CO2_kg, rcpt_weight_kg, rcpt_items_n) %>% 
  pivot_longer(cols = everything(), names_to = 'factor', values_to = 'unit') %>% 
  mutate(factor = factor(factor)) %>% 
  ggplot(aes(x=factor,y=unit)) + geom_boxplot() + facet_wrap(.~factor, scales = "free", ncol = 5)
```

### Receipt level descriptives grouped by household

```{r fig.height = 8}
#boxplots of receipt descriptives
receipt_data %>% 
  ungroup() %>%
  filter(date_recorded > hh_start) %>% #remove pre-loaded receipts
  select(day_recorded, rcpt_CO2_g_100g, rcpt_CO2_kg, rcpt_weight_kg, rcpt_items_n, household_ID) %>% 
  group_by(household_ID) %>%
  mutate(n_receipts = n_distinct(day_recorded)) %>%
  ungroup() %>%
  pivot_longer(cols = !household_ID, names_to = 'factor', values_to = 'unit') %>% 
  mutate(factor = factor(factor), household_ID = factor(household_ID)) %>% 
  ggplot(aes(x=household_ID,y=unit)) + geom_boxplot() + facet_wrap(factor~., scales = "free", ncol = 1)
```

### Household level descriptives (aggregated receipts)

```{r}
household_descriptives <-
  receipt_data %>% 
  filter(date_recorded > hh_start) %>%
  group_by(household_ID) %>%
  reframe(
    hh_CO2_kg = sum(rcpt_CO2_kg),
    hh_weight_kg = sum(rcpt_weight_kg),
    hh_items_n = sum(rcpt_items_n)
  ) %>%
  mutate(hh_CO2_g_100g = hh_CO2_kg/hh_weight_kg*100)
  
#boxplots of household descriptives
household_descriptives %>% 
  ungroup() %>%
  pivot_longer(cols = !household_ID, names_to = 'factor', values_to = 'unit') %>% 
  mutate(factor = factor(factor)) %>% 
  ggplot(aes(x=factor,y=unit)) + geom_boxplot() + facet_wrap(.~factor, scales = "free", ncol = 5)
```

## Visualize foodprint change

This considers the weight-balanced average carbon footprint of receipts.

### Time since enrollment

```{r}
#visualize receipt dates

receipt_data %>% 
  ggplot(aes(x = as.numeric(day_recorded), y = rcpt_CO2_g_100g)) +
  geom_point() +
  geom_line() +
  facet_wrap(.~household_ID) + 
  theme_light() + 
  labs(y = "Weight-adjusted average gCO2/100g", x = "Receipt date (days since start)")
```
A visual analysis does not suggest any clear change in foodprint.
Note, facet labels are the household ID.

## Sequence of receipts

```{r}
#visualize the trends
receipt_data %>% 
  ggplot(aes(x = hh_receipt_id, y = rcpt_CO2_g_100g)) +
  geom_point() +
  geom_line() +
  facet_wrap(.~household_ID) + 
  theme_light() + 
  labs(y = "Weight-adjusted average gCO2/100g", x = "Receipt number (chronological)")

#Weight-adjusted refers to the weight of individual items is factored into the calculation
#Data was loaded into the app before the participant started. This is accounted in receipt #1

```
A visual analysis does not suggest any clear change in foodprint.

## Determine whether there is statistical evidence of footprint changing over time

### Using mixed-model statistics (parametric)

#### With receipt ID as time factor

##### The model

```{r}

#mixed-model to calculate change

#center the independent variable
receipt_data$hh_receipt_id_c <- scale(receipt_data$hh_receipt_id, center = TRUE, scale = FALSE)

#full model
cat('\n\n FULL MIXED MODEL (including time factor) \n\n')
m_full <- lmer(rcpt_CO2_g_100g ~ hh_receipt_id + (1 + hh_receipt_id | household_ID), data = receipt_data)
summary(m_full)
```

##### Diagnostics (assessing heterogenity and normal distrubution of residuals)

```{r}
#investigating whether residuals are normally distibuted
densityplot(resid(m_full, scaled = TRUE))
qqPlot(resid(m_full, scaled = TRUE))
plot(m_full, household_ID ~ resid(., scaled = TRUE))
plot(m_full, type = c('p', 'smooth'))
# potential problems. Outliers in the residuals
```

There are indications of outliers and non-normality, so results should be interpreted with caution.

##### Statistical inference of time effect

```{r}
#to assess whether time was a significant factor, we need to compare it to a simpler model without the time factor

#null model (inteaction only)
m_null <- lmer(rcpt_CO2_g_100g ~ 1 + (1 | household_ID), data = receipt_data)

anova(m_null,m_full)
```
We find no indication of significance. 

#### With time since household enrollment as independent variable. 

##### The model
```{r}

#mixed-model to calculate change

#center the independent variable
# receipt_data$day_recorded_c <- scale(as.numeric(receipt_data$day_recorded), center = TRUE, scale = FALSE)

#full model
m_full <- lmer(rcpt_CO2_g_100g ~ day_recorded + (1 + day_recorded | household_ID), data = receipt_data)
summary(m_null)
```
##### Diagnostics (assessing heterogenity and normal distrubution of residuals)

```{r}
#investigating whether residuals are normally distibuted
densityplot(resid(m_full, scaled = TRUE))
qqPlot(resid(m_full, scaled = TRUE))
plot(m_full, household_ID ~ resid(., scaled = TRUE))
plot(m_full, type = c('p', 'smooth'))
# potential problems. Outliers in the residuals
```

There are indications of outliers and non-normality, so results should be interpreted with caution.

##### Statistical inference of time effect

```{r}
#null model (inteaction only)
m_null <- lmer(rcpt_CO2_g_100g ~ 1 + (1 | household_ID), data = receipt_data)

anova(m_null,m_full)
```

No significant impact of time on foodprint found.

### Using a Skillings-Mack tests (Non-parametric alternative)
```{r}
#create dataframe for ski.mack -- 'missing' observation have to be present in the df as NA
#this can easily be achieved by turning the data into a wide structure. Each row needs to be a group (household)
# https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2761045/
# https://en.wikipedia.org/wiki/Friedman_test#cite_note-6

library(Skillings.Mack)

skimack_data <- receipt_data %>% select(household_ID, hh_receipt_id, rcpt_CO2_g_100g)
# skimack_data %<>% pivot_wider(names_from = hh_receipt_id, values_from = rcpt_CO2_g_100g)
# skimack_data %<>% select(!household_ID)
# skimack_data %<>% select(!13)
# skimack_data %>% as.matrix() %>% Ski.Mack(.)
skimack_data %<>% pivot_wider(names_from = household_ID, values_from = rcpt_CO2_g_100g)
skimack_data %<>% select(!hh_receipt_id)
skimack_data %>% as.matrix() %>% Ski.Mack(.) #there is no clear difference in receipt number

# Alternatives:
# Härdle, Wolfgang, et al. “A Review of Nonparametric Time Series Analysis.” International Statistical Review / Revue Internationale de Statistique, vol. 65, no. 1, 1997, pp. 49–72. JSTOR, https://doi.org/10.2307/1403432. Accessed 22 Dec. 2023.
# http://lib.uib.kz/wp-content/uploads/2019/04/Nonlinear-Time-Series..-Nonparametric-and-Parametric-Methods-Fan-J-2003.pdf
```

The non-parametric test shows no significant impact of time.

### Paired t-test (parametric) of receipts in -1SD vs. 1SD of active scanning period

```{r}
#alternative: compare first with all future receipts
receipt_data %<>% 
  group_by(household_ID) %>%
  mutate(date_third = ceiling(round(3*day_recorded/max(as.numeric(day_recorded)), digits = 2))) %>%
  mutate(date_third = ifelse(date_third == 0, 1, date_third)) #day zero is assigned to the first third

#calculate the average footprint by third
test <- receipt_data %>% 
  group_by(household_ID, date_third) %>%
  mutate(
    period_footprint_total = sum(rcpt_CO2_kg),
    period_weight_total = sum(rcpt_weight_kg),
    period_footprint_ave = sum(rcpt_CO2_kg)/sum(rcpt_weight_kg), .after = rcpt_CO2_g_100g
  )

test <- receipt_data %>% 
  group_by(household_ID, date_third) %>%
  reframe(
    period_footprint_total = sum(rcpt_CO2_kg),
    period_weight_total = sum(rcpt_weight_kg),
    period_footprint_ave = sum(rcpt_CO2_kg)/sum(rcpt_weight_kg)
  )
```
#### Visual trends

```{r}
test %>% 
  filter(date_third != 2) %>%
  ggplot(aes(x = date_third, y = period_footprint_total, group = household_ID)) + 
  geom_line()
```

A visual analysis does not suggest any clear change in foodprint.

#### Paired t-test statistic
```{r}
ttest_data <- 
  test %>% 
  select(household_ID,date_third,period_footprint_ave) %>% 
  mutate(date_third = paste0("period.",date_third)) %>%
  pivot_wider(names_from = date_third, values_from = period_footprint_ave)

t.test(x = ttest_data$period.1, y = ttest_data$period.3, paired = T)
```

Non-significant. The is no indication of foodprint change.

```{r eval=FALSE, include=FALSE}
#---discard this. rm ANOVA does not work with 'missing' values
#https://www.theanalysisfactor.com/when-repeated-measures-anova-not-work-for-repeated-measures-data/
#test effect (repeated measures)

# library("rstatix")
receipt_data %<>% mutate(household_ID = factor(household_ID), hh_receipt_id = as.numeric(hh_receipt_id))

res.aov <- anova_test(data = receipt_data, dv = rcpt_CO2_g_100g, wid = household_ID, within = hh_receipt_id)
get_anova_table(res.aov)
```